The Right Way to Search Evolving Graphs

### 2016-01-27 paper.tex
emphasiz node activeness
timestamp -> time stamp

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Breadth First Searches Over Evolving Graphs}

@@

Treatments of evolving graphs vary in their generality and focus.
Kivel\"a \textit{et al.}~\cite{kabg14} treats time dependence as a special
case of families of graphs with multiple interrelationships.
Others like Flajolet \textit{et al.}~\cite{fkp89} use time to index the family
of related graphs, but are not concerned with explicit time-dependent processes.
Yet others focus on incremental updates to large graphs~\cite{bkmu12}.
Here, we describe evolving graphs as a time-ordered sequence of graphs, similar
to the study of metrized graphs by Tang and coworkers~\cite{ntmm13,tmml09,tsmm09,tmml10} and of 
the dynamics of communities by Grindrod, Higham and coworkers~\cite{gphe11,grihig13}.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{The Right Way to Search Evolving Graphs}

@@

Treatments of evolving graphs vary in their generality and focus.
Kivel\"a \textit{et al.}~\cite{kabg14} treats time dependence as a special
case of families of graphs with multiple interrelationships.
Others like Flajolet \textit{et al.}~\cite{fkp89} use time to index the family
of related graphs, but are not concerned with explicit time-dependent processes.
Yet others focus on incremental updates to large graphs~\cite{bkmu12}.
Here, we describe evolving graphs as a time-ordered sequence of graphs, similar
to the study of metrized graphs by Tang and coworkers~\cite{ntmm13,tmml09,tsmm09,tmml10} and of 
the dynamics of communities by Grindrod, Higham and coworkers~\cite{gphe11,grihig13}. However, we emphasize a concept called
\emph{node activeness} and we only study the active nodes on an evolving graph. 
In real-life problems, the set of active nodes is usually sparse at a given time stamp. 
Our model, as a result, can be used to model highly dynamic large evolving graph problems, where other models fail to.
